% TO COMPILE THIS RESUME: latexmk -pdf -pvc resume.tex 
\documentclass[10pt,ragged2e]{altacv}

% Change the page layout if you need to
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{biblatex}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
 
\urlstyle{same}

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Nathan Drezner}
\tagline{}
\personalinfo{
  \email{\href{mailto:nathan@plot.ly}{nathan@plot.ly}}
  \email{\href{mailto:nathan@drezner.com}{nathan@drezner.xyz}}
  \github{\href{https://github.com/ndrezn}{ndrezn}}
  \linkedin{\href{https://www.linkedin.com/in/nathan-drezner/}{Nathan Drezner}}
  \homepage{\href{https://nathandrezner.com}{nathandrezner.com}}
%   \twitter{\href{https://www.twitter.com/ndrezn}{ndrezn}}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

\cvsection[auxilleryInfo]{Plotly}
\href{https://plotly.com}{Plotly} provides graphing, analytical, and statistical tools and web frameworks for individuals and teams.
\\[8pt]

\cvevent{Technical Product Manager}{}{Oct. 2023 -- Present}{Montréal, Canada}
\begin{itemize}
\item Responsible for Dash (80m+ lifetime downloads), Plotly.py (500m+ lifetime downloads), Plotly.js, and other OSS Plotly libraries, with a focus on modernization and performance improvements
\item Launch of App Studio with features including automated code generation, large table support, theming, and task scheduling\end{itemize}

\divider

\cvevent{Manager, Professional Services}{}{Nov. 2021 -- Oct. 2023}{Montréal, Canada}
\begin{itemize}
\item Managed a team of 10+ consultants, interns, and contractors in Professional Services.
\item Developed solutions for Fortune 500 companies in various sectors including healthcare, government, energy, and technology.
\end{itemize}

\divider

\cvevent{Project Lead, Professional Services}{}{May 2021 -- Nov. 2021}{Montréal, Canada}
\begin{itemize}
\item Developed and managed client projects and established best practices in design, architecture, and performance within the Professional Services team.
\end{itemize}

\divider

\cvevent{Solutions Architect, Professional Services}{}{Feb. 2020 -- May 2021}{Montréal, Canada}
\begin{itemize}
\item Developed Dash applications using the full-stack Dash Enterprise framework.
\item Contributed to both Plotly’s open- and closed-source software projects and worked with tools including Plotly, Dash, React, Apache Spark, and Redis/Postgres.
\end{itemize}

\cvsection{Research}
\cvevent{Research Assistant}{\href{https://txtlab.org}{.txtLab} - a laboratory for cultural analytics at McGill University}{October 2018 -- May 2020}{Montréal, Canada}
\begin{itemize}
\item Studied the salient language of disagreement and consensus building on Wikipedia, overseen by Profs. Andrew Piper and Richard Jean So.
\end{itemize}

\divider

\cvevent{Research Assistant}{\href{https://mcqll.org/}{Montréal Computational \& Quantitative Linguistics Lab} - a labratory to study fundamental questions about language acquisition, processing, use in society, and change over time}{November 2019 -- May 2020}{Montréal, Canada}
\begin{itemize}
\item Studied patterns of productivity and reuse in language including designing an algorithmic implementation of a qualitative model for productivity, overseen by Prof. Timothy O'Donnell.
\end{itemize}

%\divider

\clearpage

\end{document}
